\large\bfseries Soliton Solution, B\"acklund Transformation, Conservation Laws, and rogue wave solution for a generalized variable-coefficient Sasa-Satsuma-like equation

### 2018-03-12 me/paper/paper.tex
update

\section{Lax Pair}
    The Lax pair

>>>>

\section{Lax Pair}
    The Lax pair may ensure the complete integrability of a NLEE, and can be used to obtain B\"acklund transformation, soliton solutions and conservation laws. To construct the Lax pair of Eq.(1), we extend AKNS procedure and introduce the function $a(t)$ and $b(t)$ as below,
\begin{align}
  & \Phi_{x} = U\Phi = a(t)(\lambda U_{0} + U_{1})\Phi \\
  & \Phi_{t} = V\Phi = b(t)(\lambda^{3}V_{0} + \lambda^{2}V_{1} + \lambda V_{2} + V_{3})\Phi
\end{align}
where $\Phi=(\Phi_{1}, \Phi_{2}, \Phi_{3})^{T}$, $\lambda$ is a parameter independent of $x$ and $t$, $U$ and $V$ are two $3 \times 3$ matrices, which must satisfy the compatibility condition $U_{t} - V_{x} + UV - VU = 0$.
